---
title: "First Look at NYPD CCRB data"
author:
  - Andriy Koval
  - Kyle Belanger
output:
  html_document:
    toc: true
    toc_depth: 3
    keep_md: yes
    toc_float: true
    code_folding: hide
---
This report records the initial exploration of the NYPD CCRB data as reported 
by the ProPublica ([source]( https://www.propublica.org/datastore/dataset/civilian-complaints-against-new-york-city-police-officers)).

The report also records the data cleaning actions motivated by the initial exploration. 


<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 5, 
  fig.width = 9, 
  out.width = "900px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 200
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/1-first-look/1-first-look.R") 
```

# Environment 

This section offers technical detail on the environment and data preparation. Non-technical readers should feel free to skip. 
```{r load-packages, echo=echoChunks, message=FALSE}
```

```{r load-sources, echo=echoChunks, message=FALSE}
```

```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

```{r custom-functions, echo=echoChunks, results='show', message=FALSE}
```

```{r load-data, echo=echoChunks, results='hide', message=FALSE}
```
 )
```{r inspect-data, echo=echoChunks, results='show', message=FALSE}
```

```{r tweak-data-1, echo=echoChunks, results='show', message=FALSE}
```

```{r tweak-data-2, echo=echoChunks, results='show', message=FALSE}
```

# Data

This data was obtained by [ProPublica](https://projects.propublica.org/nypd-ccrb/) through a records request made to the CCRB. It includes fully investigated allegations only for officers who were members of the department as of late June 2020 and against whom the CCRB has substantiated at least one allegation. [Read More](https://projects.propublica.org/nypd-ccrb/#about)


Note that data reported by [NY Civil Liberty Union](https://github.com/new-york-civil-liberties-union/NYPD-Misconduct-Complaint-Database) contains about 10 times more records (`323,911`) than ProPublica's (`33,358`) data presented here.  One way to think about the difference between these two data sets is to take CLU as as the universe of all allegations registerd, while ProPublica's would represent the universe of confirmed offenders.  

# Variables

We grouped the inital variables according to entity for which they store information

```{r variable-groups, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

# Officer

This section provides basic descriptive related to Members of Service (MOS, i.e. police officers)

```{r officer-1, echo=TRUE, results='show', message=F, warning=F, cache=T}
```

```{r officer-2, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

```{r officer-3, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


# Complainant

```{r complainant-1, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


```{r complainant-2, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

```{r complainant-3, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


# Complaint
```{r complaint-1, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


```{r complaint-2, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

```{r complaint-3, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


# Contact 
```{r contact-1, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


```{r contact-2, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

# Product 

After initial investigation and cleaning, the data that is passed to subsequent analysis contains:
(click on the `Code` button to unfold)

```{r tweak-data-2, echo=T, results='show', message=FALSE, eval=F}
```
```{r save-to-disk}

```


# Session Information

For the sake of documentation and reproducibility, the current report was rendered in the following environment. Click the line below to expand.

<details>

<summary>Environment </summary>

```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```


