---
title: "First Look at NYPD CCRB data"
author:
  - Andriy Koval
  - Kyle Belanger
output:
  html_document:
    toc: true
    toc_depth: 3
    keep_md: no
    toc_float: true
    code_folding: hide
  word_document:
    keep_md: no
    toc: no
---
This report records the initial exploration of the NYPD CCRB data as reported 
by the ProPublica ([source]( https://www.propublica.org/datastore/dataset/civilian-complaints-against-new-york-city-police-officers)).

The report also records the data cleaning actions motivated by the initial exploration. 


<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 5, 
  fig.width = 9, 
  out.width = "900px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 200
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/1-first-look/1-first-look.R") 
```

# Environment 

This section offers technical detail on the environment and data preparation. Non-technical readers should feel free to skip. 
```{r load-packages, echo=echoChunks, message=FALSE}
```

```{r load-sources, echo=echoChunks, message=FALSE}
```

```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

```{r custom-functions, echo=echoChunks, results='show', message=FALSE}
```

```{r load-data, echo=echoChunks, results='hide', message=FALSE}
```

```{r inspect-data, echo=echoChunks, results='show', message=FALSE}
```

```{r tweak-data-1, echo=echoChunks, results='show', message=FALSE}
```

```{r tweak-data-2, echo=echoChunks, results='show', message=FALSE}
```

# Variables

We grouped variables according to entity for which they store information

```{r variable-groups, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

# Officer

```{r officer-1, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

```{r officer-2, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

```{r officer-3, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


# Complainant

```{r complainant-1, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


```{r complainant-2, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

```{r complainant-3, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


# Complaint
```{r complaint-1, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


```{r complaint-2, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```

```{r complaint-3, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


# Contact 
```{r contact-1, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


```{r contact-2, echo=TRUE, results='show', message=FALSE, warning=FALSE, cache=T}
```


# Session Information

For the sake of documentation and reproducibility, the current report was rendered in the following environment. Click the line below to expand.

<details>

<summary>Environment </summary>

```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```


